\begin{rSection}{\textbf{Selected Projects}}

{\bf e-POS}\hfill{\hspace{2em} 

Fullstack web-based POS solution with administration feature. It was developed with NodeJs to aid gas stations in managing their sales and staff. It featured a role-based access control to ensure inventory and cash register security. It also featured keeping records of loans and an automated notification system for scheduled payments and tasks.}

{\bf Lekhoni}\\
An Android app to teach kids how to write Bengali alphabets. It has two modes, guided and unguided. In the guided mode the app will show an alphabet and a kid can draw the figure presented on the screen. In unguided mode, a kid can draw an alphabet and get feedback if it was written correctly. The feedback was calculated using a pertained OCR model for Bengali alphabets.

{\bf MediAlert}\hfill{\hspace{2em} 

An Android app for medical alerts. You can upload a prescription and your medicine routine. The app will remind you to take medicines on time.}



{\bf P2P Solution}\hfill{\hspace{2em} 

A peer-to-peer chat and file-sharing desktop app that connects two devices on the same network or devices with public IP, using their IP addresses and designated port numbers. It uses Java Socket to communicate with each other. Used OOP and Software design principles to ensure fast connectivity, data management, and modular system design.}

\end{rSection}



\section{\textbf{Projects}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {Project A: [Brief Description]}
  {Tools: [List of tools and technologies used]}
  {Month Year - Month Year}
  {{}[\href{https://github.com/your-username/project-a}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Developed [specific feature/system] for [specific purpose]
  \item Implemented [specific technology] for [specific goal], achieving [specific result]
  \item Created [specific component], ensuring [specific benefit]
  \item Applied [specific method] to analyze [specific aspect]
\resumeItemListEnd

\resumeProject
  {Project B: [Brief Description]}
  {Tools: [List of tools and technologies used]}
  {Month Year}
  {{}[\href{https://github.com/your-username/project-b}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Developed [specific model/system], achieving [specific metric]
  \item Implemented [specific feature], processing [specific volume] of data
  \item Created [specific visualization] for [specific purpose]
  \item Developed [specific component] for easy integration with [specific system]
\resumeItemListEnd

\resumeSubHeadingListEnd
