\begin{rSection}{\textbf{Leadership Experience}}
{\bf CAM SUST}{, The astronomical organization at the university.} \hfill {\ {Sylhet}}\\
Asst. Treasurer (Research \& Development) \hfill {\ Apr. '17 - Apr. '18}
\begin{itemize}
  \item \vspace{-0.5em} Looked over the finances for the club.
  \item \vspace{-0.5em} Managed sponsorships to hold Astro Olympiads and cultural programs.
  \item \vspace{-0.5em} Redesigned the membership policies and activities to increase engagement.
  \vspace{-0.3em}
\end{itemize} 

Executive Member \hfill {\ Apr. '16 - Mar. '17}
\begin{itemize}
  \item \vspace{-0.5em}  Organized weekly study sessions and competitions.
  \vspace{-0.3em}
\end{itemize} 


{\bf SUST CSE Society}{, A departmental organization for all the students and teachers.} \hfill {\ {Sylhet}}\\
Executive Member \hfill {\ Apr. '16 - Apr. '19} 
\begin{itemize}
  \item \vspace{-0.5em} Co-convened CSE Carnival 2017 featuring programming contests, robotics contests, and project showcasing.
  \vspace{-0.3em}
\end{itemize} 

General Member \hfill {\ May. '15 - Mar. '16} 
\begin{itemize}
  \item \vspace{-0.5em} Co-organized CSE Carnival 2015. 
  \vspace{-0.3em}
\end{itemize} 

{\bf Team DHUMKETU}{, A team in the inter-discipline football tournament.} \hfill {\ {Sylhet}}\\
Manager \hfill {\ Aug. '17 - Jul. '18} 
\begin{itemize}
  \item \vspace{-0.5em} Recruited and managed a team of 10 players.
  \vspace{-0.3em}
\end{itemize} 
\begin{itemize}
  \item \vspace{-0.5em} Raised funds to support the team.
  \vspace{-0.3em}
\end{itemize} 
\begin{itemize}
  \item \vspace{-0.5em} Led team to a second runner-up finish in the league championship.
  \vspace{-0.3em}
\end{itemize} 

{\bf NHSPC Boot Camp}{} \hfill {\ {Jashore}}\\
Instructor \hfill {\ Feb. '17} 
\begin{itemize}
  \item \vspace{-0.5em} Conducted several workshops on data structure and algorithms for high school students.
  \vspace{-0.3em}
\end{itemize} 
\end{rSection}